\newpage
\begin{center}
\large \bf
Zdecentralizowana aplikacja do pożyczek na platformie Ethereum
\end{center}

\section*{Streszczenie}
Projekt składa się z pracy dyplomowej oraz systemu realizującego cel postawiony w dokumencie.
Pierwszy rozdział wproawdza do technologii blockchain oraz jej implementacji, czyli Bitcoina i Ethereum. Wyjaśniona jest istota pożyczek oraz nowa metoda ich realizacji przy pomocy platformy Ethereum. Rozdział drugi przedstawia obecnie istniejące rozwiązania oraz ich silne i słabe strony. Specyfikacja wymagań oraz architektura systemu zostają nakreślone w rozdziale trzecim. Wyjaśnienie implementacji oraz dokładny opis wykorzystanych technologii następuje w rozdziale czwartym. W rodziale piątym przedstawione jest przykładowa użycie systemu.

\bigskip
{\noindent\bf Słowa kluczowe:} blockchain, Ethereum, Bitcoin, solidity, pożyczka

\vskip 2cm


\begin{center}
\large \bf
Decentralized loan application on Ethereum platform
\end{center}

\section*{Abstract}

The thesis consists of a paper and a system fulfilling the goals stated in the document. The first chapter introduces the blockchain technology and it's implementations. That is, Bitcoin and Ethereum. The concept of a loan and a novel method of loan servicing are explained. The second chapter presents the modern solutions together with their strengths and weaknesses.  The requirements specification and the architecture of the system are outlined in the third chapter. The explanation of the implementation and precise descriptions of the used technologies are given in the fourth chapter. In the fifth chapter an example usage of the system is presented.

\bigskip
{\noindent\bf Keywords:} blockchain, Ethereum, Bitcoin, solidity, pożyczka, loan

\vfill